Visualization of [fulle name] Fractional Integrals

### 2019-05-22 fractional/CMJ style files/article-template.tex
almost through geo section

\noindent
Podlubny et al. showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
\begin{equation}
\label{eq:rs}
\int_0^{t} f(\tau)~dg_t(\tau),
\end{equation}
with 
\begin{equation}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}

@@

Grobler et. al showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral. We review this conversion procedure in the Cavalieri section of this paper. Applying their approach to Eq.~\ref{eq:rs} results in:
\begin{equation}
\label{eq:cav}
\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
\end{equation}
with
\begin{equation}
a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
\end{equation}
Note, Eq.~\eqref{} is obtained by substituting Eq.~\eqref{} into Eq.~\eqref{}.

Since Eq.~\eqref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
by summing toghether the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
strip will change if either $\alpha$ or $t$ is changed. If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).

>>>>

\noindent
Podlubny et al. showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
\begin{equation}
\label{eq:rs}
\int_0^{t} f(\tau)~dg_t(\tau),
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}

@@

\noindent
Furthermore, Grobler et. al showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral. We review this conversion procedure in the Cavalieri section of this paper (see Fig.~\ref{fig:caval2}). If we apply their conversion steps to Eq.~\eqref{eq:rs} we obtain:
\begin{equation}
\label{eq:cav}
\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
\end{equation}
with
\begin{equation}
\label{eq:cav_a}
a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
\end{equation}
Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}.

\noindent
Since, Eq.~\eqref{eq:cav} is a Cavalieri integral it has a clear geometric interpretation (see Fig.~\ref{fig:caval2}). The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
by summing together the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of theses integration 
strips will change if either $\alpha$ or $t$ is changed. If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
